How to make an abridged life table and calculate life expectancy

### 2016-09-20 working_teaching_examples/how_to_abridged_life_table.Rmd
prep work for the cod decomp fx

```{r lifetable_cali_abridged}
cali.complete$group <- cut(cali.complete$ages, breaks=c(0, 1, 5, 10, 15, 20), 
                           labels = c("<1 years old", "1-4 years old", "5-9 years old", 
                                      "10-14 years old", "15 or older"), include.lowest = T, right = F)

@@

>>>>

```{r lifetable_cali_abridged, warning=F, message=F}
cali.complete$group <- cut(cali.complete$ages, breaks=c(0, 1, 5, 10, 15, 20), 
                           labels = c("<1 years old", "1-4 years old", "5-9 years old", 
                                      "10-14 years old", "15 or older"), include.lowest = T, right = F)

@@

alabama.by.strata.cod <- dat.clean.alabama %>% group_by(Year2, RaceSex, Age2) %>%
                                               arrange(RaceSex, Year2, Age2) %>%
                                               mutate(total_deaths5 = sum(Count_md5),
                                                      cod_prop_death5 = Count_md5/total_deaths5)

first.strata.cod <- alabama.by.strata.cod[alabama.by.strata$StateYearRaceSex == "Alabama.1969.White.Male", ]
